---
title: "EucFACE understorey vegetation -Summary of stats-"
author: "Shun Hasegawa"
date: "23 August 2016"
output: html_document
---

```{r setup, include=FALSE}
library(pander)
library(ggplot2)
library(grid)
knitr::opts_chunk$set(echo = TRUE)
load("../output/Data/summary_analysis.RData")
theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank()))

```

## Reanalysis using Year0 as a covariate, namely ANCOVA

Here, I reanalysed understorey vegetation data, performing ANCOVA using Year0 values as a covariate. I analysed the following variables:

* Diversity indices
    + Diversity (*H'*)
    + Evenness (*J'*)
    + Species richness (*S*)
* Dominent species
    + _Commelina cyanea_
    + _Cynodon dactylon_
    + _Microlaena stipoides_
    + _Pratia purpurascens_
* Proportion of plant functional groups
    + Grass *vs.* Forb
    + C~3\_grass~ *vs.* C~4\_grass~
    + Legume *vs.* Non-legume
    + (Native *vs.* Introduced)

Diversity indices were anlysed for all species tother, grass species only, and form species only. 

### Diversity indices

```{r div_stats, echo=FALSE, warning=FALSE}
pcol <- grep("_P$", names(div_tbl))
d <- div_tbl
d[, pcol] <- apply(d[, pcol], 2, as.numeric)
d[is.na(d)] <- 0

emphasize.italics.cols(pcol)
emphasize.strong.cells(which(d <= .1, arr.ind = TRUE))

pander(div_tbl, caption = "Diversity indices", justify = "right", split.table = Inf, keep.line.breaks = TRUE)
```

```{r div_plot, echo=FALSE, fig.cap="Fig.1 Diversity indices", fig.height=6, fig.width=6}
grid.draw(div_plot_merged)
```

## Dominent species

```{r dom_stats, echo=FALSE, warning=FALSE}
pcol <- grep("_P$", names(dom_tbl))
d <- dom_tbl
d[, pcol] <- apply(d[, pcol], 2, as.numeric)
d[is.na(d)] <- 0
emphasize.italics.cols(pcol)
emphasize.strong.cells(which(d <= .1, arr.ind = TRUE))

pander(dom_tbl, caption = "Dominent species", justify = "right", split.table = Inf, keep.line.breaks = TRUE)
```

```{r dom_plot, echo=FALSE, fig.cap="Fig.2 Dominent species", fig.height=4, fig.width=5}
fig_domspp
```

## Proportions of plant functional groups

```{r pfgprop_stat, echo=FALSE, warning=FALSE}
pcol <- grep("_P$", names(pfg_tbl))
d <- pfg_tbl
d[, pcol] <- apply(d[, pcol], 2, as.numeric)
d[is.na(d)] <- 0
emphasize.italics.cols(pcol)
emphasize.strong.cells(which(d <= .1, arr.ind = TRUE))

pander(pfg_tbl, caption = "Dominent species", justify = "right", split.table = Inf, keep.line.breaks = TRUE)

```


```{r pfgprop_plot, echo=FALSE, fig.cap="Fig.3 PFG proportion",fig.height=4, fig.width=5}
fig_pfgprop
```


