---
title: "EucFACE vegetation with environmental variables"
author: "Shun Hasegawa"
date: "Thursday, May 07, 2015"
output: pdf_document
---

# Organise environmental variables
Soil chemistry and properties such as organic matter, moisture, temperature etc. are used environmental variables. Some variables are not complete for three years. Some variables are highly correlated one another and really redundant, so they're organised before fitting to plant community data. 

```{r setup, include=FALSE}
library(knitr)
opts_knit$set(root.dir=normalizePath('../'))

```{r readchunks, include=FALSE}
read_chunk("R/Analysis.R")
read_chunk("R/FitEnvironmentalVars.R")

```{r LoadData, include=FALSE}

```{r OrganiseEnvVars, results='markup'}
```

# CAP analysis

## All species
After organising, the following variables are fitted to plant community data using Canonical analysis of principal coordinate (CAP).

* Soil moisture (moist)
* Soil temperature (temp)
* Soil organic matter (OrganicMatter)
* Depth of the hard layers (Depth_HL)
* Photosynthetically active radiation (PAR) at the forest floor (FloorPAR)

```{r RunCap, results='markup', fig.width=6, fig.height=6}
```

There was a significant association between soil variables and plant community. Ring 1 and 2 are high temperature and dry soil. Ring 3 and 4 are wet and low organic matter. Ring 5 and 6 are wet and higher soil organic matter. Also yearly changes ($\bigcirc\rightarrow\triangle\rightarrow\Box$) of plant community may be associated with temperature changes.

Adjacent FACE rings (1\&2, 3\&4, 5\&6), or rings within a block, seems to have same similar soil characteristics and associated plant community. This masks CO$_2$ effects, hence, using Partial CAP, between-block variation is removed and re-performed CAP with CO$_2$ and year as treatments.

## Partial CAP
```{r RunPartialCap, results='markup', fig.width=6, fig.height=6, message=FALSE}
```

As expected block accounts for major proportion of variation (55\%). Ambient and eCO$_2$ were clearly split and Year2013 is separated from Year2014 and Year2015. This indicates that plant community changed from the 1st year to the 2nd year, but not much between the 2nd and 3rd years. Also difference between CO$_2$ treatments are likely to be due to initial difference which is highly associated with environmental variables.

## Run CAP for each CO$_2$ treatments
Due to the initial difference in plant community between CO$_2$ treatments, it's hard to see CO$_2$ effects. So I performed CAP each CO$_2$ treatments separately and see the yearly changes. In order to take the initial difference into account, between-ring variation is removed and residual is analysed using partial CAP.

```{r RunCAPbyCO2_AllSpp, results='markup'}
```

There was a significant association between yearly changes and plant communities, but as expected large proportion of variation is due to between-ring difference (80 and 77\% in ambient and eCO$_2$ rings, respectively.)

![CAP with all species for each CO2](../output/figs/FACE_CAPvsYear_byCO2.pdf)

## Plant functional groups
Plant functional group composition is also analysed.

```{r RunCAPbyCO2_PFG, results='markup', fig.width=6, fig.height=6}
```
