---
title: "EucFACE understorey vegetation -Summary of stats-"
author: "Shun Hasegawa"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  # html_document:
  #   toc: true
  word_document:
    toc: true
---

```{r setup, include=FALSE}
library(pander)
library(ggplot2)
library(grid)
library(plyr)
library(dplyr)
library(tidyr)
library(MuMIn)
library(visreg)
library(lmerTest)
knitr::opts_chunk$set(echo = TRUE)
load("../output/Data/summary_analysis.RData")
load("../output/Data/AllObj.RData")
theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank()))

```

*Note that the coneficients presented here that were estimated using bootstarap were not finalised yet, so they should be checked again for convergent issues*

# Introduction

Here, I reanalysed understorey vegetation data, performing ANCOVA using Year0 values as a covariate for univariate analysis. Multivariate anlayses were removed now (PRC and MDS). I analysed the following variables for univariate analysis:

* Diversity indices
    + Diversity (*H'*)
    + Evenness (*J'*)
    + Species richness (*S*)
* Abundance
    + Subordinate C~4~
    + Dominant C~4~
    + Subordiante C~3~
    + Dominant C~3~
* Ratios of plant functional groups
    + C4:C3 ratios
    + Subordinate:dominant ratios
* Multiple regression analysis 
    + Log annual rates of change (LAR) with einvironmental variables (Moist, Temp, PAR)
        + Subordinate C~4~
        + Dominant C~4~
        + Subordiante C~3~
        + Dominant C~3~
    +C4:C3 ratios against soil nitrogen and phorphorus availability





# Overview of observed species

```{r spp_tbl, echo=FALSE}
pander(spp_year_summary, caption = "The number of species for each PFG")


pander(spp_co2_summary, caption = "The number of species for each CO2 treatment. Total number of species for each treatment (tot_), uniquely found ones (uni_) and commonly found in both CO2 treatments (common)", justify = "right")

pander(pfg_cov_summary, caption = "% coverage of each PFG")

pander(tail(spp_cov_summary, n = 10), caption = "% coverage of top 10 species")
```



# Univariate analysis (ANCOVA)

## Summary results

```{r summary_stats, echo=FALSE, warning=FALSE}
all_tbl <- all_tbl[order(all_tbl$report, decreasing = TRUE), ]
pcol <- grep("_P$", names(all_tbl))
d <- all_tbl
d[, pcol] <- apply(d[, pcol], 2, as.numeric)
d[is.na(d)] <- 0

emphasize.italics.cols(pcol)
emphasize.strong.cells(which(d <= .1, arr.ind = TRUE))
row.names(all_tbl) <- NULL
pander(all_tbl, caption = "Summary of repeated measures ANOVA", justify = "right", split.table = Inf, keep.line.breaks = TRUE)
```


## Diversity indices


```{r div_plot, echo=FALSE, fig.cap="Fig.1 Diversity indices. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.", fig.height=6, fig.width=6}
grid.draw(div_mplot)
```


```{r div_tbl, echo=FALSE}
names(div_tbl_l) <- c("Diversity", "Evenness", "Species richness")
l <- llply(names(div_tbl_l), function(x) pander(div_tbl_l[[x]], caption = x, justify = "right"))
l[[1]]
l[[2]]
l[[3]]
```




## Abundance of dominant, subordinate C3 and C4 species


```{r abund_plot, echo=FALSE, fig.cap="Fig.2 Abundance of dominant and subordinate C3 and C4 species. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.", fig.height=5.5, fig.width=5}
sd_abund_fig
```


```{r abund_tbl, echo=FALSE}
l  <- dlply(sd_adjMean_tble, .(PFG, type), function(x) x[, -c(1, 2)])
l2 <- llply(names(l), function(x) pander(l[[x]], caption = x, justify = "right"))
l2[[1]]
l2[[2]]
l2[[3]]
l2[[4]]
```



## Proportions of plant functional groups


```{r pfgprop_plot, echo=FALSE, ,fig.cap="Fig.3 C4:C3 ratio. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.",fig.height=3, fig.width=2}
fig_c43
fig_sd
```


# Annual rates of change in C~4~ and C~3~ abundance
Here, I examined the effects of eCO~2~ on annual rates of change in C~3~ and C~4~ abundance in relation to understorey temperature, PAR and soil moisture. I tested CO~2~ and interactions between CO~2~ and the others.


## C4 graminoid


```{r c4_model_summary, echo=FALSE, results='asis', message=FALSE}
lc4    <- dlply(filter(coeftbl_all, PFG == "c4"), .(type))
lc4tbl <- llply(names(lc4), function(x) pander(lc4[[x]][, -c(1, 2)], caption = x, justify = "right"))
lc4tbl[[1]]
lc4tbl[[2]]
lc4tbl[[3]]

pander(ldply(list('all' = c4d_m2, 
               'subordinate' = lar_sd_c34_ml$subordinate_c4,
               'dominant' = lar_sd_c34_ml$dominant_c4),
      r.squared), 
      justify = "right", caption = "model summary")

```


```{r c4_partial_regerssion_plot, echo=FALSE, results='asis', fig.width=5, fig.height=5}
create_resplot(c4d_m2, 
               ylab = expression(Adj.~annual~rates~of~change~"in"~C[4]),
               ylim <- c(-2, 2.6))
```


## C3 graminoid


```{r c3_model_summary, echo=FALSE, results='asis', message=FALSE}
lc3    <- dlply(filter(coeftbl_all, PFG == "c3"), .(type))
lc3tbl <- llply(names(lc4), function(x) pander(lc4[[x]][, -c(1, 2)], caption = x, justify = "right"))
lc3tbl[[1]]
lc3tbl[[2]]
lc3tbl[[3]]

pander(ldply(list('all' = c3d_m2, 
               'subordinate' = lar_sd_c34_ml$subordinate_c3,
               'dominant' = lar_sd_c34_ml$dominant_c3),
             r.squared),
       justify = "right", caption = "model summary")

```


```{r c3_partial_regerssion_plot, echo=FALSE, results='asis', fig.width=5, fig.height=5}
create_resplot(c3d_m2, 
               ylab = expression(Adj.~annual~rates~of~change~"in"~C[3]),
               ylim <- c(-2.5, 1.5))
```


# Relationship between C~4~:C~3~ ratios and soil Na nd P availability
```{r c43r_soilNP, echo=FALSE, results='asis', message=FALSE}
rid <- data.frame(RI = c43_soil_coef_impo) %>% 
  mutate(predictor = row.names(.),
         RI = round(RI, 3))

c43soil_tbl <- ldply(list('90CI' = c43_soil_coef_90, '95CI' = c43_soil_coef), function(x){
  d <- cbind(summary(c43_soil)$coef[, "Estimate"], x[3:5, ])
  colnames(d) <- c("estimate", "lwr", "upr")
  dd <- data.frame(d) %>% 
    mutate(predictor = row.names(.)) %>% 
    mutate_each(funs(round(., 3)), estimate, lwr, upr) %>% 
    transmute(predictor, coefs = paste0(estimate, " [", lwr, ", ", upr, "]"))
  return(dd)
}) %>% 
  spread(.id, coefs) %>% 
  left_join(rid)
pander(c43soil_tbl, caption = "C4:C3 ratios vs soil N and P", justify = "right")


pander(r.squared(c43_soil), caption = "model summary", justify = "right")

```

```{r c43soil_fig, fig.width=4, fig.height=4, echo=FALSE}
plot(s_c43_r ~ s_n, c43_ratio_iem, col = co2, pch = 19, ylab = "C4:C3 ratios", 
     xlab = "Soil N availability")
legend("topright", legend = levels(c43_ratio_iem$co2), col = c(1, 2), pch = 19, bty = 'n')
```




# Appendix

## Species coverage
```{r sp_cov_tbl, echo=FALSE, results='asis'}
pander(spp_cov_summary)
```

