---
title: "EucFACE understorey vegetation -Summary of stats-"
author: "Shun Hasegawa"
date: "`r format(Sys.time(), '%d %B, %Y')`"
output:
  # html_document:
  #   toc: true
  word_document:
    toc: true
    reference_docx: EucFACE_understorey_vegetation_summary_analysis_ed.docx
---

```{r setup, include=FALSE}
library(pander)
library(ggplot2)
library(grid)
library(plyr)
library(dplyr)
library(tidyr)
library(MuMIn)
library(visreg)
library(lmerTest)
knitr::opts_chunk$set(echo = TRUE)
load("../output/Data/summary_analysis.RData")
load("../output/Data/AllObj.RData")

# confirmed coefficients (no convergent errorr while bootstrapping)
load("../output/Data/coef_c43ratio.RData")
load("../output/Data/coef_dc3_env.RData")
load("../output/Data/coef_dc4_env.RData")
load("../output/Data/coef_sc3_env.RData")
load("../output/Data/coef_sc4_env.RData")

theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank()))

```

*Note that the coneficients presented here that were estimated using bootstarap were not finalised yet, so they should be checked again for convergent issues*

# Introduction

Here, I reanalysed understorey vegetation data, performing ANCOVA using Year0 values as a covariate for univariate analysis. Multivariate anlayses were removed now (PRC and MDS). I analysed the following variables for univariate analysis:

* Diversity indices
    + Diversity (*H'*)
    + Evenness (*J'*)
    + Species richness (*S*)
* Abundance
    + Subordinate C~4~
    + Dominant C~4~
    + Subordiante C~3~
    + Dominant C~3~
* Ratios of plant functional groups
    + C4:C3 ratios
    + Subordinate:dominant ratios
* Multiple regression analysis 
    + Log annual rates of change (LAR) with einvironmental variables (Moist, Temp, PAR)
        + Subordinate C~4~
        + Dominant C~4~
        + Subordiante C~3~
        + Dominant C~3~
    +C4:C3 ratios against soil nitrogen and phorphorus availability





# Overview of observed species

```{r spp_tbl, echo=FALSE}
pander(spp_year_summary, caption = "The number of species for each PFG")


pander(spp_co2_summary, caption = "The number of species for each CO2 treatment. Total number of species for each treatment (tot_), uniquely found ones (uni_) and commonly found in both CO2 treatments (common)", justify = "right")

pander(pfg_cov_summary, caption = "% coverage of each PFG")

pander(tail(spp_cov_summary, n = 10), caption = "% coverage of top 10 species")

sb_tbl <- veg_FullVdf %>% 
  filter(form == "Grass") %>% 
  left_join(grass_df[, c("species", "type")], by = c("variable" = "species")) %>% 
  mutate(type = ifelse(is.na(type), "transient", type)) %>% 
  group_by(PFG, type) %>% 
  summarise(value = sum(value)) %>% 
  ungroup() %>% 
  mutate(prop = value / sum(value),
         prop = round(prop * 100, 1))
pander(sb_tbl, caption = "Summary of dominant ands subordinat species of graminoids",
       justify = "right")

```


```{r forb_summary, echo=FALSE, results='markup'}
f_df <- veg_FullVdf %>% 
  filter(form == "Forb") %>% 
  group_by(year, variable) %>% 
  summarise(value = sum(value)) %>% 
  ungroup() %>% 
  filter(value > 0)

f_y0 <- f_df$variable[f_df$year == "Year0"]
f_y123 <- unique(f_df$variable[f_df$year != "Year0"])

spring_spp <- length(setdiff(f_y0, f_y123))
summer_spp <- length(setdiff(f_y123, f_y0))
common_spp <- length(intersect(f_y123, f_y0))

pander(data.frame(spring = spring_spp, summer = summer_spp, cmmon = common_spp),
       caption = "The number of forb species found in the spring and summer surveys")

```



# Univariate analysis (ANCOVA)

## Summary results

```{r summary_stats, echo=FALSE, warning=FALSE}
all_tbl <- all_tbl[order(all_tbl$report, decreasing = TRUE), ]
pcol <- grep("_P$", names(all_tbl))
d <- all_tbl
d[, pcol] <- apply(d[, pcol], 2, as.numeric)
d[is.na(d)] <- 0

emphasize.italics.cols(pcol)
emphasize.strong.cells(which(d <= .1, arr.ind = TRUE))
row.names(all_tbl) <- NULL
pander(all_tbl, caption = "Summary of repeated measures ANOVA", justify = "right", split.table = Inf, keep.line.breaks = TRUE)

```


## Diversity indices


```{r div_plot, echo=FALSE, fig.cap="Fig.1 Diversity indices. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.", fig.height=6, fig.width=6}
grid.draw(div_mplot)
```


```{r div_tbl, echo=FALSE}
names(div_tbl_l) <- c("Diversity", "Evenness", "Species richness")
l <- llply(names(div_tbl_l), function(x) pander(div_tbl_l[[x]], caption = x, justify = "right"))
l[[1]]
l[[2]]
l[[3]]
```




## Abundance of dominant, subordinate C3 and C4 species


```{r abund_plot, echo=FALSE, fig.cap="Fig.2 Abundance of dominant and subordinate C3 and C4 species. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.", fig.height=5.5, fig.width=5}
sd_abund_fig
```


```{r abund_tbl, echo=FALSE}
l  <- dlply(sd_adjMean_tble, .(PFG, type), function(x) x[, -c(1, 2)])
l2 <- llply(names(l), function(x) pander(l[[x]], caption = x, justify = "right"))
l2[[1]]
l2[[2]]
l2[[3]]
l2[[4]]
```



## Proportions of plant functional groups


```{r pfgprop_plot, echo=FALSE, ,fig.cap="Fig.3 C4:C3 ratio. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.",fig.height=3, fig.width=2}
fig_c43
fig_sd
```



# Relationship between C~4~:C~3~ ratios and soil N and P availability
```{r c43r_soilNP, echo=FALSE, results='asis', message=FALSE}
rid <- data.frame(RI = c43_soil_coef_impo) %>%
  mutate(predictor = row.names(.),
         RI = round(RI, 3))

c43soil_tbl <- ldply(list('90CI' = c43_soil_coef_90, '95CI' = c43_soil_coef), function(x){
  d <- cbind(summary(c43_soil_m2)$coef[, "Estimate"], x[4:9, ])
  colnames(d) <- c("estimate", "lwr", "upr")
  dd <- data.frame(d) %>%
    mutate(predictor = row.names(.)) %>%
    mutate_each(funs(round(., 3)), estimate, lwr, upr) %>%
    transmute(predictor, coefs = paste0(estimate, " [", lwr, ", ", upr, "]"))
  return(dd)
}) %>%
  spread(.id, coefs) %>%
  left_join(rid)

# model summary
pander(c43soil_tbl, caption = "C4:C3 ratios vs soil N and P", justify = "right")
pander(r.squared(c43_soil_m2), caption = "model summary", justify = "right")


```

```{r c43soil_modelinfo, echo=TRUE, results='markup'}
# variance components
VarCorr(c43_soil_m2)

# multicollinearity
car::vif(lm(s_c43_r ~ s_n + s_p + s_moist + s_temp + s_par, data = c43_ratio_iem))

```


```{r c43soil_fig, fig.width=5.5, fig.height=5, echo=FALSE}
plot_c43r_np()
```




# Appendix

## Species coverage
```{r sp_cov_tbl, echo=FALSE, results='asis'}
pander(spp_cov_summary)
```

