---
title: "EucFACE understorey vegetation -Summary of stats-"
author: "Shun Hasegawa"
date: "22 September 2016"
output: html_document
---

```{r setup, include=FALSE}
library(pander)
library(ggplot2)
library(grid)
knitr::opts_chunk$set(echo = TRUE)
load("../output/Data/summary_analysis.RData")
load("../output/Data/summary_rda.RData")
theme_set(theme_bw() + 
            theme(panel.grid.major = element_blank(), 
                  panel.grid.minor = element_blank()))

```

## Reanalysis

Here, I reanalysed understorey vegetation data, performing ANCOVA using Year0 values as a covariate for univariate analysis and redundancy analysis (RDA) for multivariate analysis. I analysed the following variables for univariate analysis:

* Diversity indices
    + Diversity (*H'*)
    + Evenness (*J'*)
    + Species richness (*S*)
* Dominant species
    + _Commelina cyanea_
    + _Cynodon dactylon_
    + _Microlaena stipoides_
    + _Pratia purpurascens_
* Proportion of plant functional groups
    + Grass *vs.* Forb
    + C~3\_grass~ *vs.* C~4\_grass~
    + Legume *vs.* Non-legume
    + (Native *vs.* Introduced)

Diversity indices and RDA were analysed for all species together, grass species only, and form species only. 

## Univariate analysis (ANCOVA)

### Diversity indices

```{r div_stats, echo=FALSE, warning=FALSE}
pcol <- grep("_P$", names(div_tbl))
d <- div_tbl
d[, pcol] <- apply(d[, pcol], 2, as.numeric)
d[is.na(d)] <- 0

emphasize.italics.cols(pcol)
emphasize.strong.cells(which(d <= .1, arr.ind = TRUE))

pander(div_tbl, caption = "Diversity indices", justify = "right", split.table = Inf, keep.line.breaks = TRUE)
```

```{r div_plot, echo=FALSE, fig.cap="Fig.1 Diversity indices. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.", fig.height=6, fig.width=6}
grid.draw(div_plot_merged)
```

### Dominent species

```{r dom_stats, echo=FALSE, warning=FALSE}
pcol <- grep("_P$", names(dom_tbl))
d <- dom_tbl
d[, pcol] <- apply(d[, pcol], 2, as.numeric)
d[is.na(d)] <- 0
emphasize.italics.cols(pcol)
emphasize.strong.cells(which(d <= .1, arr.ind = TRUE))

pander(dom_tbl, caption = "Dominent species", justify = "right", split.table = Inf, keep.line.breaks = TRUE)
```

```{r dom_plot, echo=FALSE, fig.cap="Fig.2 Dominent species. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.", fig.height=5.5, fig.width=5}
fig_domspp
```

### Proportions of plant functional groups

```{r pfgprop_stat, echo=FALSE, warning=FALSE}
pcol <- grep("_P$", names(pfg_tbl))
d <- pfg_tbl
d[, pcol] <- apply(d[, pcol], 2, as.numeric)
d[is.na(d)] <- 0
emphasize.italics.cols(pcol)
emphasize.strong.cells(which(d <= .1, arr.ind = TRUE))

pander(pfg_tbl, caption = "Dominent species", justify = "right", split.table = Inf, keep.line.breaks = TRUE)

```


```{r pfgprop_plot, echo=FALSE, fig.cap="Fig.3 PFG proportion. Black points depict mean values adjusted by Year0 values with 95% CI. Gray points depict observed values for each FACE ring.",fig.height=5.5, fig.width=5}
fig_pfgprop
```


## Multivariate analysis (RDA)

Hellinger transformation was applied to species data to improve asymmetric distribution of species abundance.

```{r rda_mod_table, echo=FALSE}
pander(rda_model_tbl, justify = "right", split.table = Inf, 
       caption = "Table 4. RDA models for each plant form (all species, forbs and grasses). Final models were obtained following simplification of full models. The values shown in this table are adjusted R^2 with statistically significant codes: P <.1 (.), <.05([*]), <.01([**]) and <.001([***])")


# bold adjusted R2 fro terms used in full model
fd_col <- grep("_Fdf$", names(all_model_results_tbl))  # col for fd
d <- all_model_results_tbl
bold_ind <- which(d != "-", arr.ind = TRUE)            # if fd == "-", the terms are not used in the full model
bold_ind <- bold_ind[bold_ind[, "col"] %in% fd_col, ]  # index for cells to be bolded
bold_ind[, "col"] <- bold_ind[, "col"] - 1             # adjrR is placed left of fd
emphasize.strong.cells(bold_ind)

pander(all_model_results_tbl, justify = "right", split.table = Inf, caption = "Table 5. Summary results of RDA analysys for each plant form (all species, forbs and grasses). Adjusted R^2 for single terms (adjR) are shown in bold for the terms used in the full models. Marginal F values for the terms remained in the parsimonious models after model simplification are shown with associated statistically significant codes (P <.1 (.), <.05([*]), <.01([**]) and <.001([***])). The terms that were removed by model simplification are shown as 'rm'")

```

```{r rda_plot, echo=FALSE, fig.cap="Fig.4 Results of RDA analysis. Important predictors identified above were fitted to a whole 4-year dataset for each form. Individual FACE ring is connected with a line over study years. The number alongside the points in Year0 depict FACE ring numbers.", fig.width=6.5, fig.height=6}
grid.draw(rda_plot_merged)
```

