---
title: "Inspection of vegetation data in September and December 2012"
author: "Shun Hasegawa"
date: "Tuesday, May 12, 2015"
output: pdf_document
---

In the 1st year vegetation survey was conducted twice: September and December 2012. When these data are merged and used as the 1st year data, more species are found compared to the 2nd and 3rd year. It's likely to be because September data includes spring species. In order to solve this issue, I visually inspect the whole data and see the following three possible solutions.
1. Use only December 2012 data
2. Combine September ad December, and use only dominant spp
3. Combine September ad December, and use only species observed in the 2nd the 3rd years.

```{r, include=FALSE}
source("../R/Packages.R")
load("../output//Data/FACE_Vegetation_Raw_2013_2015_PreInspection.RData")

vdf.mlt <- melt(vdf, id = c("year", "month", "ring", "plot", "position", "cell"))

# Combine Sep and Dec
DF2013 <- subset(vdf.mlt, year == 2013)
# combine sep and dec and remove duplicates
DF2013_merged <- DF2013 %>%
  group_by(variable, year, ring, plot, position, cell) %>%
  summarise(value = sum(value, na.rm = TRUE))

# Remove double count
DF2013_merged$value[which(DF2013_merged$valu == 2)] <- 1
DF2013_merged$month <- factor("Sep_Dec")

# Create a new data frame containing Dec2013, S+D2013, 2014 and 2015
VegRes15_SD <- rbind.fill(subset(vdf.mlt, month == "December"), DF2013_merged)
```

Firstly, plot all data for each year. For the 1st year, December data and also Sep-Dec-merged data are plotted. 

```{r, echo=FALSE, fig.width=8, fig.height=8}
# Create a barplot for each year
VegRes15_SD$ym <- with(VegRes15_SD, year:month)

# Yearly sum
VegRes15_YearSum <- ddply(VegRes15_SD, .(ym, variable), summarise, value = sum(value))

# Reorder accoridng to abundance
Total_sum <- ddply(subset(VegRes15_YearSum, ym != "2013:December"), 
                   .(variable), 
                   summarise, value = sum(value))
OderedSpp <- Total_sum$variable[order(Total_sum$value, decreasing = TRUE)]

VegRes15_YearSum$variable <- factor(VegRes15_YearSum$variable, levels = OderedSpp)

# Barplot
theme_set(theme_bw())
p <- ggplot(VegRes15_YearSum, aes(x = variable, y = value))
p2 <- p + geom_bar(stat = "identity") + 
  facet_grid(ym ~ .) + 
  theme(axis.text.x = element_text(angle = 90))
p2
```

Using only Dec doesn't seem to be a good idea as I loose quite many dominant herb species compared to 2014 and 2015.

Zoom in to see minor species.

```{r, echo=FALSE, fig.width=8, fig.height = 8}
# Zoom in to see minor spp
p2 + coord_cartesian(ylim = c(0, 50))
  # surely there are more spp in 2013:Sep_Dec than 2014 and 2015, but many of
  # them are observed only <5 cells
```

Surely there are more species in 2013:Sep_Dec than 2014 and 2015, but many of them are observed only <5 cells. Let's see only dominant species. Below, I plotted only those species which had been observed more than 1% and 5% of total cells (100 x 4 x 6 = 2400).

```{r, echo=FALSE, fig.width=8, fig.height = 8}
# Plot only dominant spp
PlotDominantSpp <- function(coverage, dfs = VegRes15_YearSum){
  # coverage: percentage coverage for threshhold. Spp below this is removed
  tdf <- ddply(dfs, .(ym), mutate, 
               Dominant = ifelse(value > coverage * 2400, TRUE, FALSE))
  
  # Spp which coveres >1% at least one of three years
  DominantSpp <- unique(tdf$variable[tdf$Dominant])
  
  p <- ggplot(subset(tdf, variable %in% DominantSpp), aes(x = variable, y = value))
  p2 <- p + geom_bar(stat = "identity") + 
    facet_grid(ym ~ ., scale = "free_x") + 
    theme(axis.text.x = element_text(angle = 90)) +
    ggtitle(paste0(">", coverage * 100, "% coverage species"))
  return(p2)
}

# 1 %
PlotDominantSpp(coverage = 0.01)

# 5 %
PlotDominantSpp(coverage = 0.05)
```

5 % seems to cut too many species. Removeing <1% coverage species may be suitable.
